Exploring probability distributions for bivariate temporal granularities

### 2019-11-20 main.Rmd
Relationship between circular granularities

>>>>

Relationship between circular granularities:

In general, any circular granularity relating two linear granularity, none of which are bottom granularity can be expressed as

$$C_{(G, H)}(z) = G(\lfloor z/k(BG,G) \rfloor\mod k(G,H))$$

where, linear granularity H is periodic with respect to  linear granularity G and k(G, H) represents the period length of G within H.

If linear granularities are not provided or bottom granularity is not known, any circular granularities of order m, provided the circular granularities till order (m-1) are provided.
